Stable Hot Spot Analysis (Draft)

### 2017-06-15 paper-main.tex
row of images

\begin{figure*}[htp]
  \centering

  \begin{tabular}{cccccccc}
    \hline
    \multicolumn{8}{l}{Multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
    \includegraphics[width=4.6em]{images/gen-rawdata-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \hline
    \multicolumn{8}{l}{G*Multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-8}
  \end{tabular}

\end{figure*}

>>>>

\begin{figure*}[htp]
  \centering
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
    \includegraphics[width=4.6em]{images/gen-rawdata-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{G* Multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Focal G* Multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
  \end{tabular}

  \includegraphics[width=.48\linewidth]{images/gen-zoom-sohup-1}
  \hspace{1em}
  \includegraphics[width=.48\linewidth]{images/gen-zoom-sohdown-1}

  \caption{
    This image shows all aggregation levels for G* and Focal G* together 
    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
  }
\end{figure*}
